### 2016-05-27 syntax.tex
hacking on syntax

Fix a nonempty sets $U,\Sigma$ and integers $k,m_1,m_2,n>0$ with $m_1 \leq m_2$.  Fix a symbol $\bot \not\in U$.  An $(n,k,[m_1,m_2])$-filter (over universe~$U$) is a tuple  $B=(\mathsc{Hash},\mathsc{Rep},\mathsc{Qry},\mathsc{Up}, \mathsc{Test})$.   
%
The randomized \emph{hash-sampling} algorithm~$\mathsc{Hash}$ samples a size~$k$ subset~$\mathcal{H} \subset \mathrm{Func}(U,\{0,1,\ldots,m_2-1\})$.  We write $\mathcal{H} \getsr \mathsc{Hash}$ for this operation.
%
The deterministic representation algorithm $\mathsc{Rep}\colon [U]^n \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m\right)$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
%
The determinisitc query algorithm $\mathsc{Qry}\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times U \rightarrow \bits^*$ takes a representation $M$ and an element $x \in U$ and returns a bitstring.  
%
The deterministic \emph{update} algorithm $\mathsc{Up}\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times \bits^* \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \cup \{\bot\}$ takes a representation and an update string, and returns an updated representation or the distinguished symbol~$\bot$. 
%
The deterministic \emph{test} algorithm $\mathsc{Test} \colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \times U \rightarrow \bits$ takes a representation~$M$ and an element~$x \in U$ and returns a bit.
%
We assume that all $\mathsc{Rep},\mathsc{Qry},\mathsc{Up},\mathsc{Test}$ all have blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.

>>>>

Fix a nonempty sets $U,\Sigma$ and integers $k,m_1,m_2,n>0$ with $m_1 \leq m_2$.  Fix a symbol $\bot \not\in U$.  An $(n,k,[m_1,m_2])$-filter (over universe~$U$) is a tuple  $B=(\mathsc{Hash},\mathsc{Rep},\mathsc{Qry},\mathsc{Up}, \mathsc{Test})$.   
%
The randomized \emph{hash-sampling} algorithm~$\mathsc{Hash}$ samples a size~$k$ subset~$\mathcal{H} \subset \mathrm{Func}(U,\{0,1,\ldots,m_2-1\})$.  We write $\mathcal{H} \getsr \mathsc{Hash}$ for this operation.
%
The deterministic representation algorithm $\mathsc{Rep}\colon [U]^n \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m\right)$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
%
The determinisitc query algorithm $\mathsc{Qry}\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times U \rightarrow \bits^*$ takes a representation $M$ and an element $x \in U$ and returns a bitstring.  
%
The randomized \emph{update} algorithm $\mathsc{Up}\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times \bits^* \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \cup \{\bot\}$ takes a representation and an update string, and returns an updated representation or the distinguished symbol~$\bot$.  \tsnote{I allow randomized update to admit things like the ``Stable Bloom filter'' construction, which has a randomized forgetting feature.  Other constructions may have something similar.}
%
The deterministic \emph{test} algorithm $\mathsc{Test} \colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \times U \rightarrow \bits$ takes a representation~$M$ and an element~$x \in U$ and returns a bit.
%
We assume that all $\mathsc{Rep},\mathsc{Qry},\mathsc{Up},\mathsc{Test}$ all have blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.
